\documentclass[12pt,a4paper,twoside]{article}

\input{preamble}

\begin{document}

\input{titlepage_progressreport}
\newpage
\thispagestyle{empty}
\cleardoublepage
\newpage

\section{Summary}

Two weeks since the inception of the start of the project, our group has:

\begin{itemize}
	\item Implemented most of the backend.
	\item Implemented a basic user interface for the frontend and developed visualisations for use.
\end{itemize}

These will be elaborated in the following sections.

\section{Components}

\subsection{Data retrieval component}
This server-side component has been implemented in Java using the Jersey RESTful Web Services framework with a MySQL database. It is currently running on Google App Engine at \texttt{http://money-world.appspot.com} with a simple API to obtain data in JSON format.

The component executes SQL queries on the MySQL database to obtain Java objects, which are further marshalled into JSON output according to a schema.

The aggregator has not been implemented; currently the database contains only data from the World Bank. Event data for countries will be added to enhance visualisations.

The database schema is as follows:

\begin{itemize}
	\item \textbf{Country} CountryCode, CountryName, Region, IncomeGroup, CountryNotes
	\item \textbf{DataSet} DataSetCode, DataSetName, DataSetNotes, Source
	\item \textbf{DataPoint} DataSetCode, CountryCode, Year, Value,
	\item \textbf{Visualisation} VisualisationID, Type, ExtraData
	\item \textbf{VisualisationCountry} VisualisationID, CountryCode
	\item \textbf{VisualisationDataSet} VisualisationID, DataSetCode
	\item \textbf{Comment} CommentID, CommentBody, CommentUser, VisualisationID, Created, ExtraData
	\item \textbf{CountryCode} CountryCode2, CountryCode3
\end{itemize}

\subsection{Data explanation component}
Not implemented yet (as per project plan).

\subsection{Data visualisation component}

\subsection{Comment display and input component}
Not implemented yet (as per project plan).

\subsection{Comment storage component}
Not implemented yet (as per project plan).

\subsection{Sharing component}
Not implemented yet (as per project plan).

\subsection{UI and UX component}
The frontend runs on the Sencha Touch framework and Cordova to run on Android phones. A basic user interface has been implemented that can easily incorporate visualisations. Basic user details can be stored and retrieved for the application's purposes (country, region).

Further improvements required are styling and theming of the interface, with extra graphics and icons to enhance the apperance.

The frontend is build according to the Model-View-Controller (MVC framework). As of writing, the components are:

\begin{itemize}
	\item \textbf{Models} Setting, Country
	\item \textbf{Views} Init, Main, Settings, Overview, DetailedView, ComparisonView, MainTileView, MapView
	\item \textbf{Controllers} Init, Main, Settings, Overview, MainTileView, MapView
	\item \textbf{Stores} Settings, Countries
\end{itemize}

\end{document}
